A search for high-mass black holes in data from the second LIGO observing run using a Bayesian ranking-statistic

### 2021-05-26 main.tex

\begin{figure}[!ht]
{\centering \includegraphics[width=0.85\linewidth]{images/reweighted_bcr_cdf_smaller_legend.png} }
\caption[BCR distribution example]{Histograms represent the survival function (1-CDF) from our high-mass selection of background triggers (gray) and simulated signals (blue) triggers obtained from \pycbc's search of data from $\text{August 13 - 21, 2017}$. Vertical lines mark the $\text{ln}\ \bcr$ of \IAS's GW170817A and \GWTC's GW170814. \avi{Adjust to have same fonts as other plots} }\label{fig:bcrCdf}
\end{figure}

@@

\begin{figure*}
    \centering
    \begin{subfigure}
        \centering
        \includegraphics[width=0.45\linewidth]{170222_prior_posterior.png}
    \end{subfigure}
    ~ 
    \begin{subfigure}
        \centering
        \includegraphics[width=0.45\linewidth]{170222_source_posterior.png}
    \end{subfigure}
    \caption{Posterior distributions for some parameters of 170222, comparing posteriors in orange and prior probability density functions to the one-dimensional marginal distributions in green. 
    Left: Posterior probability distributions for 4 of the 11 search parameters. Sections of the prior probability density functions used for analysis are displayed in green in one-dimensional marginal distributions plots.
    Right: Posterior probability distributions for some inferred parameters. \avi{Right plot labels being cut off. Should i plot prior-samples on the right? }
    \label{fig:170222}}
\end{figure*}

>>>>

\begin{figure}[!ht]
{\centering \includegraphics[width=0.85\linewidth]{images/reweighted_bcr_cdf_smaller_legend.png} }
\caption[BCR distribution example]{Histograms represent the survival function (1-CDF) from our high-mass selection of background triggers (gray) and simulated signals (blue) triggers obtained from \pycbc's search of data from $\text{August 13 - 21, 2017}$. Vertical lines mark the $\text{ln}\ \bcr$ of \IAS's GW170817A and \GWTC's GW170814.}\label{fig:bcrCdf}
\end{figure}

@@

\begin{figure*}
    \centering
    \begin{subfigure}
        \centering
        \includegraphics[width=0.45\linewidth]{170222_prior_posterior.png}
    \end{subfigure}
    ~ 
    \begin{subfigure}
        \centering
        \includegraphics[width=0.45\linewidth]{170222_source_posterior.png}
    \end{subfigure}
    \caption{Posterior distributions for some parameters of 170222. 
    Left: Posterior probability distributions for 4 of the 11 search parameters. Sections of the prior probability density functions used for analysis are displayed in green in one-dimensional marginal distributions plots.
    Right: Posterior probability distributions for some inferred parameters. \avi{Should i plot prior-samples on the right? }
    \label{fig:170222}}
\end{figure*}
